Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-02-16 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
Gabriel's edits

Apart from providing a powerful diagnostic tool in determining if the approxiamtion is sufficiently accurate, equations in previous Section~\ref{sec_num_equations} also give the optimal values for $m$ (the minimum $m$ required for an accurate approximation) and $c$ (the minimum $c$ that allows for the minimum $m$) that allow to spend minimum computations.

Guidelines for updating $m$ and/or $c$ must be provided:

>>>>

Apart from providing a powerful diagnostic tool in determining if the approxiamtion is sufficiently accurate, equations in previous Section~\ref{sec_num_equations} also give the optimal values for $m$ (the minimum $m$ required for an accurate approximation) and $c$ (the minimum $c$ that allows for the minimum $m$) that allow to minimizing the computational cost.

Guidelines for updating $m$ and/or $c$ are:
